Paper TITLE

### 2016-08-08 paper/Paper.Rmd
Removed titles and added figures

```{r, echo = F}
clean_years <- read_csv("../clean_data/clean_years.csv")

@@

```{r, include = F}
url <- "http://www.mapsofworld.com/usa/usa-maps/united-states-regional-maps.html"
html <- read_html(url)
xpath <- '//table[@class="tableizer-table"]'

@@

```{r, echo = FALSE}
clean_years %>% 
  # Group and summarise the amount of people in each poverty group each year
  group_by(fmtincrelpovcat, year) %>%
  summarise(count = n()) %>%
  # Clean NAs
  na.omit() %>%
  # Group again by year to calculate relative percentages per year
  group_by(year) %>% 
  mutate(percent = count / sum(count),  
         # Clean the labels
         fmtincrelpovcat = factor(fmtincrelpovcat, 
                                  levels = c("1 LTE Poverty", 
                                             "2 100-150% Poverty", 
                                             "3 150-200% Poverty", 
                                             "4 200%+ Poverty"),  
                                  labels = c("Less than poverty income",   
                                             "100-150% of poverty income",   
                                             "150-200% of poverty income",    
                                             "> 200% of poverty income"),
                                  ordered = T)) %>% 
  ggplot(aes(x = year, 
             y = percent,
             fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.8) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(title = "Amount of households relative to poverty line",
       x = "Year",
       y = "Percent of households",
       fill = "Household income
relative to poverty income") +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()
```

@@

```{r, echo = FALSE}
###### Household Income
  ####overall graph
clean_years %>% 
  select(zinc2, year, region, fmtburden)%>% 
  filter(fmtburden != ".", fmtburden != "4 No Income") %>% 
  mutate(fmtburden = str_replace(fmtburden, "Greater than 50%", "50% or More")) %>% 
  group_by_("year", "fmtburden") %>%  
  summarise_(new_y = as.formula(
  paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income", x = "Year", color = "Burden") +
  scale_y_continuous(limits=c(0,NA),breaks=c(0,20000,40000,60000),labels=function(x){paste0(x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, echo = FALSE, fig.cap=" "}
 ### faceted by region 
clean_years %>%  
  mutate(fmtburden = str_replace(fmtburden, "Greater than 50%", "50% or More")) %>%
  filter(fmtburden != "4 No Income") %>% 
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) +
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden") +
  scale_y_continuous(limits=c(0,NA),breaks=c(0,25000,50000,75000),labels=function(x){paste0(x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, echo = FALSE}

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(title = "Relationship between Monthly \nHousing Costs and Burden", 
       y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, echo= FALSE}

### faceted by region
  cleanyearsmonthly %>%  
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zsmhc", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) + 
  labs(title = "Relationship between Monthly \nHousing Costs and Burden", 
       y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, fig.width=12, fig.height=6,echo = F, message=F,error=F, warning=FALSE}
clean_years %>% 
  filter(fmtstructuretype != ".") %>% 
      # Use NSE
      group_by_("year", "fmtstructuretype") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","increlamipct", ",na.rm=T)"))) %>%  
      # Use NSE
      ggplot(aes_string(x = "year",   
                        y = "new_y",   
                        colour = "fmtstructuretype")) +  
  geom_line(size = 1) +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  labs(title="Income compared to area's median grouped by house type",
       colour = "Structure Type",
       y="Income percentage of area median income",
       x = "Year") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, fig.width=12, fig.height=6, echo = F, message=F,error=F, warning=FALSE}
assisted = clean_years %>% filter(!is.na(assisted)) %>% 
      # Use NSE
      group_by_("assisted", "fmtcostmedrelamicat") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","burden", ",na.rm=T)"))) %>% 
      ungroup %>% 
      mutate(assisted = as.factor(assisted))
ggplot(assisted, aes(y = new_y,   
                  x = fmtcostmedrelamicat,
                  fill = assisted, group = assisted)) +  
  geom_bar(
           stat="identity") + 
  labs(title="Burden based on Median housing cost with assistance",
       y="Burden",
       x = "",
       fill="Assistance") + 
  scale_y_continuous(limits=c(0,1), labels=function(x){paste0(x*100, "%")}) +
  scale_x_discrete(labels = function(x){str_replace_all(x,"^[0-9](.*)","\\1")}) +
  scale_fill_brewer("Assistance", 
                    labels = c("Without Assistance", 
                               "With Assistance"),
                    palette = "Set2")  +
  coord_flip() +
  theme_tufte()
```

@@

```{r, echo = FALSE}
clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  mutate(region=as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) + 
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor the Number of People by Region") + 
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2", 
                      name = "Region", 
                      labels = regionNames) +
  theme_tufte()

@@

```{r, echo = F}
clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  mutate(region = as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor Number of Bedrooms by region") +
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2",
                      name = "Region", 
                      labels = regionNames) +
  theme_tufte()

>>>>

```{r, echo = F, fig.cap="Median Burden across Years and Household sizes"}
clean_years <- read_csv("../clean_data/clean_years.csv")

@@

```{r, include = F, fig.cap="Median Income across Census Regions"}
url <- "http://www.mapsofworld.com/usa/usa-maps/united-states-regional-maps.html"
html <- read_html(url)
xpath <- '//table[@class="tableizer-table"]'

@@

```{r, echo = FALSE, fig.cap="Amount of households relative to poverty line"}
clean_years %>% 
  # Group and summarise the amount of people in each poverty group each year
  group_by(fmtincrelpovcat, year) %>%
  summarise(count = n()) %>%
  # Clean NAs
  na.omit() %>%
  # Group again by year to calculate relative percentages per year
  group_by(year) %>% 
  mutate(percent = count / sum(count),  
         # Clean the labels
         fmtincrelpovcat = factor(fmtincrelpovcat, 
                                  levels = c("1 LTE Poverty", 
                                             "2 100-150% Poverty", 
                                             "3 150-200% Poverty", 
                                             "4 200%+ Poverty"),  
                                  labels = c("Less than poverty income",   
                                             "100-150% of poverty income",   
                                             "150-200% of poverty income",    
                                             "> 200% of poverty income"),
                                  ordered = T)) %>% 
  ggplot(aes(x = year, 
             y = percent,
             fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.8) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(x = "Year",
       y = "Percent of households",
       fill = "Household income
relative to poverty income") +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()
```

@@

```{r, echo = FALSE, fig.cap="Relationship between Household Income and Burden"}
###### Household Income
  ####overall graph
clean_years %>% 
  select(zinc2, year, region, fmtburden)%>% 
  filter(fmtburden != ".", fmtburden != "4 No Income") %>% 
  mutate(fmtburden = str_replace(fmtburden, "Greater than 50%", "50% or More")) %>% 
  group_by_("year", "fmtburden") %>%  
  summarise_(new_y = as.formula(
  paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(y = "Household Income", x = "Year", color = "Burden") +
  scale_y_continuous(limits=c(0,NA),breaks=c(0,20000,40000,60000),labels=function(x){paste0(x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, echo = FALSE, fig.cap="Relationship between Household Income and Burden"}
 ### faceted by region 
clean_years %>%  
  mutate(fmtburden = str_replace(fmtburden, "Greater than 50%", "50% or More")) %>%
  filter(fmtburden != "4 No Income") %>% 
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zinc2", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) +
  labs(y = "Household Income ($)", x = "Year", color = "Burden") +
  scale_y_continuous(limits=c(0,NA),breaks=c(0,25000,50000,75000),labels=function(x){paste0(x/1000, "K")}) +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, echo = FALSE, fig.cap = "Relationship between Monthly Housing Costs and Burden"}

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  labs(y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, echo= FALSE, fig.cap="Relationship between Monthly Housing Costs and Burden"}

### faceted by region
  cleanyearsmonthly %>%  
  group_by_("year","region", "fmtburden") %>%  
  summarise_(new_y = as.formula(
    paste0("~ median(","zsmhc", ",na.rm=T)"))) %>% 
  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line(size = 1) + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) + 
  labs(y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, fig.width=12, fig.height=6,echo = F, message=F,error=F, warning=FALSE, fig.cap = "Income compared to area's median grouped by house type"}
clean_years %>% 
  filter(fmtstructuretype != ".") %>% 
      # Use NSE
      group_by_("year", "fmtstructuretype") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","increlamipct", ",na.rm=T)"))) %>%  
      # Use NSE
      ggplot(aes_string(x = "year",   
                        y = "new_y",   
                        colour = "fmtstructuretype")) +  
  geom_line(size = 1) +
  scale_y_continuous(labels=function(x){paste0(x*100, "%")}) +
  labs(colour = "Structure Type",
       y="Income percentage of area median income",
       x = "Year") +
  scale_colour_brewer(palette = "Dark2") +
  theme_tufte()

@@

```{r, fig.width=12, fig.height=6, echo = F, message=F,error=F, warning=FALSE, fig.cap="Burden based on Median housing cost with assistance"}
assisted = clean_years %>% filter(!is.na(assisted)) %>% 
      # Use NSE
      group_by_("assisted", "fmtcostmedrelamicat") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","burden", ",na.rm=T)"))) %>% 
      ungroup %>% 
      mutate(assisted = as.factor(assisted))
ggplot(assisted, aes(y = new_y,   
                  x = fmtcostmedrelamicat,
                  fill = assisted, group = assisted)) +  
  geom_bar(
           stat="identity") + 
  labs(y="Burden",
       x = "",
       fill="Assistance") + 
  scale_y_continuous(limits=c(0,1), labels=function(x){paste0(x*100, "%")}) +
  scale_x_discrete(labels = function(x){str_replace_all(str_replace_all(x, "^[0-9] (.*)","\\1"), "LTE (.*)","<= \\1")}) +
  scale_fill_brewer("Assistance", 
                    labels = c("Without Assistance", 
                               "With Assistance"),
                    palette = "Set2")  +
  coord_flip() +
  theme_tufte()
```

@@

```{r, echo = FALSE, fig.cap="Median Income Adjusted for the Number of People by Region"}
clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  mutate(region=as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) + 
  labs(x = "Year", y = "Median Adjusted Income (per persons)") + 
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2", 
                      name = "Region", 
                      labels = regionNames) +
  theme_tufte()

@@

```{r, echo = F, fig.cap="Median Income Adjusted for Number of Bedrooms by region"}
clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  mutate(region = as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) +
  labs(x = "Year", y = "Median Adjusted Income (per persons)") +
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2",
                      name = "Region", 
                      labels = regionNames) +
  theme_tufte()
